\documentclass{article}

\begin{document}
    \section{General Questions}

    \subsection{Are the objectives interesting to the target audience?}

    The target audience can be taxi drivers, taxi passengers and managers of taxi market. Taxi drivers may want to know where to find 
    passengers at different times. Passengers may want to get information about a specific trip such as trip time and trip cost. Managers
    of taxi market may want to adjust the regulation of taxi market according to demands and supplies. 

    \subsection{Is the scope of the project appropriate? If not, suggest improvements.}

    Yes, it is. However, it can be specilized into only one specific scope such as only for taxi passengers, taxi drivers or managers of taxi market. 

    \subsection{Is the split between optimal and must-have features appropriate? Why?}

    Yes, we split between optimal and must-have features according to how important the information is and how interested target audiences would be.

    \subsection{Is the visualization innovative? Creative? Why?}

    Yes, the topic is innovative and creative. However, we may use many exsited visualization forms. I think we will provide a useful tool for both drives and passengers.

    \section{Visual Encoding}

    \subsection{Does the visualization scale to the used dataset? Could it handle larger but similar datasets?}

    The visualization scales to the used dataset. It can also handle other kind of dataset like buses dataset and train dataset.

    \subsection{Is the project plan detailed enough? Is a path to the final project clear?}

    The project plan is detailed enough. Fisrt of all, we will build the frame of the view port and gather needed dataset. Then, we will
    focus on extracting features from dataset. Next, we will implement the visualization based on features extracted. Finally, we will improve 
    the appearance of the visualization and add optional features.

    \subsection{Is an interesting story told?}

    Yes, we tend to demomenstrate the need to change the regulation of traditional taxi market.

    \subsection{Dose the visualization follow the principles used in class?}

    Yes, we design the visualization according to the principles mentioned in class.

    \subsection{What is the primary visual encoding? Does it match to the most important aspect of the data?}

    Primary visual encoding: map. We intend to display the spatial misallocation of taxi market, so it match to the most important aspect of the data.

    \subsection{Is color sensibly used? If not, suggest improvements.}

    Yes.

    \section{Interaction and Animation}

    \subsection{Is the interaction meaningful? If not, suggest improvements.}

    Yes.

    \subsection{If multiple views, are they coordinated? If not, would it be meaningful?}

    Multiple views are coordinated.

    \subsection{Is there any animation planned? Is it clear? Is it intuitive?}

    No, we don't implement any animation yet.

\end{document}